A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Beam Dynamics

### 2018-07-11 paper/theor-experiment.tex
fixing figures of tba beam line

\begin{figure}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig1) at (0,0)
	{\includegraphics[width=\textwidth]{Report/awa-drawing}};
	\node[fill=white, inner sep=2pt] (txt2) at (0,20) {Gun};
	\node[fill=white, inner sep=2pt] (txt2) at (20,20) {Accelerating Cavities};
	\node[fill=white, inner sep=2pt] (txt2) at (88,28) {Quadrupoles};
	\draw [blue, ->, line width=1] (99,28) -- (99, 21);
	\node[fill=white, inner sep=2pt] (txt2) at (125,10) {$s_2$};
	\node[fill=white, inner sep=2pt] (txt2) at (112,8) {$s_1$};
	\node[fill=white, inner sep=2pt] (txt2) at (115,30) {Kicker};
	\draw [blue, ->, line width=1] (120,30) -- (120, 23);	
	\end{tikzpicture}
	\caption{Side view of the high charge linac at the AWA. 
		All hardware in this drawing is currently installed.}
	\label{awa-linac}
\end{figure}

\begin{figure}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig2) at (0,0)
	{\includegraphics[width=\textwidth]{Report/tba_dogleg}};
	\node[fill=white, inner sep=2pt] (txt2) at (2,35) {$s_1$};
	\node[fill=white, inner sep=2pt] (txt2) at (14,35) {$s_2$};
	\node[fill=white, inner sep=2pt] (txt2) at (33,31) {$s_3$};
	\node[fill=white, inner sep=2pt] (txt2) at (24,50) {Septum};
	\draw [blue, ->, line width=1] (30,50) -- (30, 42);	
	\node[fill=white, inner sep=2pt] (txt2) at (3,50) {Kicker};
	\draw [blue, ->, line width=1] (9.5,50) -- (9.5, 43);
	\end{tikzpicture}
	\caption{Continuation of the high charge beam line layout at the AWA, top view. 
		This is the proposed two beam acceleration section.}
	\label{awa-tba}
\end{figure}
%
%\vspace{-1em}

@@

The maximum number of individuals per generation was fixed at 80, 
Each experiment was allowed to run for twenty four hours, with 
a maximum generation limit of 100. 
We reduced the seven objectives to the four needed to construct 
the Pareto fronts that would be the final goal of this study.
The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)\text{, } \text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$. 
\lsnote{You could define $\varepsilon_{x1}$ to be $\varepsilon_{x} (s=s1)$ and similarly in the table and then use going forward to simplify notation}
The optimization parameters specific to OPAL input for ex-3 are given as an example.
Note the design variables defined in Section \ref{awaproblem}
precede the optimization parameters in the OPAL input file.
%
\vspace{0.2cm}
\begin{Verbatim}[fontsize=\scriptsize]
OPTIMIZE, INPUT="tmpl/optLinac_40nC.tmpl",
OUTPUT="optLinac_40nC",
OUTDIR="results",
OBJECTIVES = {rmss1, rmsx1, emitx1, de1, rmss2, rmsx2, emitx2},
DVARS = {dv0, dv1, dv2, dv3, dv4, dv5, dv6, dv7},
CONSTRAINTS = {c1, c2},
INITIALPOPULATION=656,
MAXGENERATIONS=200,
NUM_MASTERS=1,
NUM_COWORKERS=8,
SIMTMPDIR="tmp",
TEMPLATEDIR="tmpl",
FIELDMAPDIR="fieldmaps",
NUM_IND_GEN=328,
GENE_MUTATION_PROBABILITY=0.8,
MUTATION_PROBABILITY=0.8,
RECOMBINATION_PROBABILITY=0.2;
QUIT;
\end{Verbatim}
\vspace{0.2cm}

>>>>

\def \gunheight {25}
\def \quadheight {35}
\def \quadleft {127}
\def \kickerleft {160}
\def \leftarrow{10}
\def \bottomofarrows {29}
\def \topofarrows {34}
\begin{figure*}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig1) at (0,0)
	{\includegraphics[width=\textwidth]{Report/awa-drawing}};
	\node[fill=white, inner sep=2pt] (txt2) at (0,\gunheight) {\large Gun};
	\node[fill=white, inner sep=2pt] (txt2) at (20,\gunheight) {\large Accelerating Cavities};
	\node[fill=white, inner sep=2pt] (txt2) at (\quadleft,\quadheight) {\large Quadrupoles};
	\draw [blue, ->, line width=1] (\quadleft+\leftarrow,\topofarrows) -- (\quadleft+\leftarrow, \bottomofarrows);
	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft,20) {\large $s_1$};
	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft+8,20) {\large $s_2$};
	\node[fill=white, inner sep=2pt] (txt2) at (\kickerleft,\quadheight) {\large Kicker};
	\draw [blue, ->, line width=1] (\kickerleft+\leftarrow-3,\topofarrows) -- (\kickerleft+\leftarrow-3, \bottomofarrows);	
	\draw [black, ->, line width=1] (0,-2) -- (100, -2);
	\node[fill=white, inner sep=2pt] (txt2) at (50,0) {\large Beam Direction};
	\end{tikzpicture}
	\caption{Side view of the high charge linac at the AWA. 
		All hardware in this drawing is currently installed.}
	\label{awa-linac}
	\vspace{-7em}
\end{figure*}

\def \septheight {65}
\def \bottomarrow {57}
\def \kleft {13}
\def \sleft {41.5}
\def \sheight {47}
\def \beam {32}
\begin{figure*}
	\begin{tikzpicture}[every node/.style={anchor=south west,inner sep=0pt},x=1mm, y=1mm,]   
	\node (fig2) at (0,0)
	{\includegraphics[width=\textwidth]{Report/tba_dogleg}};
	\node[fill=white, inner sep=2pt] (txt2) at (3,\sheight) {\large $s_1$};
	\node[fill=white, inner sep=2pt] (txt2) at (20,\sheight) {\large $s_2$};
	\node[fill=white, inner sep=2pt] (txt2) at (46,45) {\large $s_3$};
	\node[fill=white, inner sep=2pt] (txt2) at (33,\septheight) {\large Septum};
	\draw [blue, ->, line width=1] (\sleft,\septheight) -- (\sleft, \bottomarrow);	
	\node[fill=white, inner sep=2pt] (txt2) at (7,\septheight) {\large Kicker};
	\draw [blue, ->, line width=1] (\kleft,\septheight) -- (\kleft, \bottomarrow);
	\draw [black, ->, line width=1] (0,\beam) -- (100,\beam);
	\node[fill=white, inner sep=2pt] (txt2) at (50,\beam+2) {\large Beam Direction};
	\end{tikzpicture}
	\vspace{-10em}
	\caption{Continuation of the high charge beam line layout at the AWA, top view. 
		This is the proposed two beam acceleration section. 
		Only the kicker in this drawing is installed}
	\label{awa-tba}
\end{figure*}
%
%\vspace{-1em}

@@

The maximum number of individuals per generation was fixed at 80, 
Each experiment was allowed to run for twenty four hours, with 
a maximum generation limit of 100. 
We reduced the seven objectives to the four needed to construct 
the Pareto fronts that would be the final goal of this study.
The objectives include: $\varepsilon_{x}\left(s = s_1\right)\text{, } \varepsilon_{x}\left(s = s_2\right)\text{, } \text{rms}_{s}\left(s = s_1\right)\text{, and }  \text{rms}_{s}\left(s = s_2\right)$. 
\lsnote{You could define $\varepsilon_{x1}$ to be $\varepsilon_{x} (s=s1)$ and similarly in the table and then use going forward to simplify notation}
The optimization parameters specific to OPAL input for ex-3 are given as an example.
Note the design variables defined in Section \ref{awaproblem}
precede the optimization parameters in the OPAL input file.
%

\vspace{0.2cm}
\begin{Verbatim}[fontsize=\scriptsize]
OPTIMIZE, INPUT="tmpl/optLinac_40nC.tmpl",
OUTPUT="optLinac_40nC",
OUTDIR="results",
OBJECTIVES = {rmss1, rmsx1, emitx1, de1, rmss2, rmsx2, emitx2},
DVARS = {dv0, dv1, dv2, dv3, dv4, dv5, dv6, dv7},
CONSTRAINTS = {c1, c2},
INITIALPOPULATION=656,
MAXGENERATIONS=200,
NUM_MASTERS=1,
NUM_COWORKERS=8,
SIMTMPDIR="tmp",
TEMPLATEDIR="tmpl",
FIELDMAPDIR="fieldmaps",
NUM_IND_GEN=328,
GENE_MUTATION_PROBABILITY=0.8,
MUTATION_PROBABILITY=0.8,
RECOMBINATION_PROBABILITY=0.2;
QUIT;
\end{Verbatim}
\vspace{0.2cm}
